### 2025-07-12 machine-learning.qmd
20250712 - documentation

@@

@@

Below, we fit a linear regression model with one predictor and evaluate it with [cross-validation](#sec-crossValidation).
We also evaluate its accuracy on the hold-out (test) data.

@@

@@

The random forest models were fit using the `ranger` package [@R-ranger; @Wright2017_packages].

>>>>

We set up the *k* folds using the `group_vfold_cv()` function of the `rsample` package [@R-sample].

@@

We set up the LOO folds using the `loo_cv()` function of the `rsample` package [@R-sample].

@@

Below, we fit a linear regression model with one predictor and evaluate it with [cross-validation](#sec-crossValidation).
We also evaluate its accuracy on the hold-out (test) data.
For each of the models, we fit and evaluate the models using the `tidymodels` ecosystem of packages [@R-tidymodels; @Kuhn2020_packages].
we specify our model formula using the `recipe()` function of the `recipes` package [@R-recipes].
We define the model using the `linear_reg()`, `set_engine()`, and `set_mode()` functions of the `parsnip` package [@R-parsnip].
We specify the workflow using the `workflow()`, `add_recipe()`, and `add_model()` functions of the `workflows` package [@R-workflows].
We fit the cross-validation model using the `fit_resamples()` function of the `tune` package [@R-tune].
We specify the accuracy metrics to evaluate using the `metric_set()` function of the `yardstick` package [@R-yardstick].
We fit the final model using the `fit()` function of the `workflows` package [@R-workflows].
We evaluate the accuracy of the model's predictions on the test data using the `accuracyOverall()` of the [`petersenlab`](https://github.com/DevPsyLab/petersenlab) package [@R-petersenlab].

@@

For the machine learning models, we perform the parameter tuning using the `tune()`, `tune_grid()`, `select_best()`, and `finalize_workflow()` functions of the `tune` package [@R-tune].
We specify the grid of possible parameter values using the `grid_regular()` function of the `dials` package [@R-dials].

@@

The random forest models were fit using the `ranger` package [@R-ranger; @Wright2017_packages].
We specify the grid of possible parameter values using the `grid_random()`, `update.parameters()`, `mtry()`, and `min_n()` functions of the `dials` package [@R-dials] and the `extract_parameter_set_dials()` function of the `hardhat` package [@R-hardhat].
